\begin{problem}{Arithmetic Sequence}{standard input}{standard output}{1 second}{256 megabytes}

    In an Arithmetic Sequence the difference between one term and the next is a constant. In other words, we just add the same value each time ... infinitely.

    In General we could write an arithmetic sequence like this: ${a, a+d, a+2d, a+3d, ... }$ where $a$ is the first term, and $d$ is the difference between the terms (called the \textsl{common difference})
    
    To product the terms of this arithmetic sequence: ${a \times (a+d) \times (a+2d) \times (a+3d) \times ...}$ Use this formula: $\prod_{k=0}^{n-1}(a+kd)=\frac{ad^{n-1}\Gamma(n+\frac{a}{d})}{\Gamma(1+\frac{a}{d})}$
    
    Now you are given a number $n$, print two totally different arithmetic sequences \textbf{of integers} with length $n$ and same products.
    
    Note: \textbf{totally different} means that there shouldn't be any number appear twice in the two sequences.
\InputFile
The test case only contains an integer $n(2\le n \le 100)$, represents the length of the required arithmetic sequence.
\OutputFile
Two lines. Each line consists of $n$ integers seperated by a space.

The first line represents an arithmetic 
sequence $a_0, a_1, a_2, ..., a_{n-1}$.

The second line represents another arithmetic sequence $b_0, b_1, b_2, ..., b_{n-1}$.

Ensure $\prod_{i=0}^{n-1}a_i=\prod_{i=0}^{n-1}b_i$ and each number in $a_0, a_1, ..., a_{n-1}, b_0, b_1, ..., b_{n-1}$ is unique.

\Example

\begin{example}
\exmpfile{example.1.in}{example.1.ans}%
\exmpfile{ex2.in}{ex2.ans}%
\end{example}

\Notes

Welcome to CCPC-CC.

\end{problem}
